---
title: "Lines of Intent"
subtitle: "Every Border Was Someone's Decision"
author: "Naresh Saginala"
date: today
date-format: "MMMM D, YYYY"
format:
  html:
    embed-resources: true
    theme: flatly
    toc: true
    toc-title: "Contents"
    toc-depth: 2
    toc-location: left
    code-fold: true
    code-summary: "Show code"
    code-tools: false
    fig-align: center
    smooth-scroll: true
    highlight-style: github
execute:
  echo: true
  warning: false
  message: false
---

## Overview

*Borders are not natural facts. They were drawn by people, in rooms, on specific dates — and they can be redrawn.*

This visualization animates political border changes across three regions of the world: **Central Europe** (1914–2000), the **Middle East** (1920–2003), and **Post-colonial Africa** (1938–1993). Each region is shown across six key historical moments — treaties, wars, independence movements, and collapses of empire.

Each panel draws countries one-by-one using a hand-rendered sketchy aesthetic via the `roughsf` package, reinforcing the central argument: every line on a political map is a human decision, provisional and erasable. The interactive widget below lets you step through each region at your own pace.

---

## Data and methods

**Data:** `cshapes` R package (Weidmann, Kusa & Gleditsch, 2010) — historically accurate country boundaries for every date from 1886 to present.

**Rendering:** `roughsf` (Schoch, 2022) — converts sf geometries to hand-drawn sketchy paths via the `rough.js` engine. Roughness 1.4, bowing 0.8.

**Palette:** MetBrewer `Redon` — muted earth tones derived from Odilon Redon's botanical illustrations.

**Concept:** The hand-drawn aesthetic is the argument. Borders rendered in pencil look provisional, erasable, human. Every line on a political map was drawn by a person and can be redrawn by another.

---

## Setup

All packages loaded in a single block. `cshapes` provides historically accurate country boundaries. `roughsf` converts geometries to hand-drawn paths. `MetBrewer` supplies the Redon earth-tone palette.

```{r setup}
#| code-fold: false
library(cshapes)
library(roughsf)
library(sf)
library(ggplot2)
library(MetBrewer)
library(htmltools)
library(webshot2)
library(gifski)
library(dplyr)
library(jsonlite)
library(geojsonsf)
library(htmlwidgets)
library(png)

# roughsf uses randomness to generate sketch strokes — seed ensures reproducible output
set.seed(42)

# Ensure Chromium is available for webshot2 — required for roughsf → PNG rendering
tryCatch(
    chromote::find_chrome(),
    error = function(e) {
        message("Chromium not found — installing via chromote::install_chrome()")
        chromote::install_chrome()
    }
)

dir.create("outputs", showWarnings = FALSE)
dir.create("outputs/frames", showWarnings = FALSE)
```

## Region Definitions

Each region is defined by a bounding box, a set of historical dates, and an annotation for each panel explaining what changed and why.

```{r define_regions}
regions <- list(
    central_europe = list(
        label = "Central Europe",
        bbox = st_bbox(
            c(xmin = 6, ymin = 43, xmax = 33, ymax = 57),
            crs = st_crs(4326)
        ),
        years = c(1914, 1919, 1938, 1945, 1990, 2000),
        dates = as.Date(c(
            "1914-07-01", "1919-12-01", "1938-10-01",
            "1945-09-01", "1990-12-01", "2000-01-01"
        )),
        annotations = c(
            "1914" = "Four empires. Almost no internal borders.",
            "1919" = "Treaty of Versailles - empire shatters into six new states.",
            "1938" = "Munich Agreement - Germany absorbs Austria and Sudetenland.",
            "1945" = "Potsdam Agreement - Germany split in two. Poland shifts west. Europe redrawn by victors.",
            "1990" = "German reunification Oct 3 1990. Yugoslavia begins fracturing.",
            "2000" = "Yugoslav wars conclude. 6 new states where one stood. 14 more borders than 1914."
        )
    ),
    middle_east = list(
        label = "Middle East",
        bbox = st_bbox(
            c(xmin = 25, ymin = 15, xmax = 65, ymax = 42),
            crs = st_crs(4326)
        ),
        years = c(1920, 1932, 1948, 1967, 1991, 2003),
        dates = as.Date(c(
            "1920-08-01", "1932-01-01", "1948-05-15",
            "1967-06-10", "1991-03-01", "2003-04-01"
        )),
        annotations = c(
            "1920" = "San Remo Conference. Sykes-Picot lines become League of Nations mandates.",
            "1932" = "Iraq granted independence - the first Arab state carved from Ottoman collapse.",
            "1948" = "Israeli independence - borders disputed immediately.",
            "1967" = "Six-Day War - territorial control shifts in six days.",
            "1991" = "Gulf War ceasefire Feb 28. Kuwait liberated. Iraq's borders hold - for now.",
            "2003" = "Iraq War - another redrawing begins."
        )
    ),
    africa = list(
        label = "Post-colonial Africa",
        bbox = st_bbox(
            c(xmin = -25, ymin = -35, xmax = 55, ymax = 40),
            crs = st_crs(4326)
        ),
        years = c(1938, 1955, 1960, 1965, 1975, 1993),
        dates = as.Date(c(
            "1938-01-01", "1955-01-01", "1960-12-01",
            "1965-01-01", "1975-12-01", "1993-06-01"
        )),
        annotations = c(
            "1938" = "Berlin Conference lines hold. Only Ethiopia and Liberia are independent.",
            "1955" = "Bandung Conference. African leaders demand independence - inside colonial borders.",
            "1960" = "Year of Africa. 17 nations born. The lines stay. Only the flags change.",
            "1965" = "Decolonisation accelerates. New nations inherit borders drawn without them.",
            "1975" = "Portuguese empire retreats. Angola, Mozambique, Cape Verde born.",
            "1993" = "50 independent states rendered — 4 small islands outside dataset coverage. Almost every border unchanged from 1884. The lines outlasted the empires."
        )
    )
)
```

## Rendering Functions

Two rendering pipelines: `roughsf` → `webshot2` for the hand-drawn look, with a clean `ggplot2` fallback if Chromium is unavailable. `roughsf` cannot handle `MULTI*` geometries, so all features are cast to `POLYGON` before rendering.

```{r rendering_functions}
# Gleditsch-Ward (GW) state system codes — numeric IDs assigned to each country.
# Each region is filtered by a contiguous gwcode range covering that area.
GW_REGIONS <- list(
    central_europe = c(200, 399),
    middle_east    = c(630, 699),
    africa         = c(400, 626)
)
# GW_EXTRA: Gleditsch-Ward codes for countries that fall inside the bounding box
# but lie outside the primary GW_REGIONS numeric range — added manually to ensure
# complete coverage (e.g. Egypt gwcode=651 spans both Africa and Middle East ranges)
GW_EXTRA <- list(
    central_europe = integer(0),
    middle_east    = c(640, 645, 651, 652, 660, 663, 666, 667, 669, 670, 678, 680, 690, 694, 696, 698),
    africa         = c(651)
)
get_region_sf <- function(date, bbox, region_key = NULL) {
    world <- cshp(date = date, useGW = TRUE)
    world <- st_transform(world, 4326)
    world <- st_make_valid(world)
    if (!is.null(region_key) && region_key %in% names(GW_REGIONS)) {
        rng <- GW_REGIONS[[region_key]]
        extra <- GW_EXTRA[[region_key]]
        world <- world[(world$gwcode >= rng[1] & world$gwcode <= rng[2]) |
            world$gwcode %in% extra, ]
        message("  gwcode [", rng[1], "-", rng[2], "]: ", nrow(world), " countries")
    }
    bbox_p <- st_as_sfc(bbox)
    # suppressWarnings: st_intersection warns about attribute assumptions on geometries — safe to ignore
    region <- suppressWarnings(st_intersection(world, bbox_p))
    region <- region[!st_is_empty(region), ]
    st_make_valid(region)
}

panel_theme <- function() {
    theme_void() +
        theme(
            plot.title = element_text(
                family = "serif", size = 13, hjust = 0.5,
                margin = margin(b = 4), color = "#3d3530"
            ),
            plot.caption = element_text(
                family = "serif", size = 8, hjust = 0.5,
                color = "#9a8e88", margin = margin(t = 6)
            ),
            plot.margin = margin(10, 10, 10, 10),
            plot.background = element_rect(
                fill = "#fff8f2", color = "#e0d8d0",
                linewidth = 0.4
            )
        )
}

render_panel <- function(sf_data, year_label, annotation,
                         palette_name = "Redon",
                         roughness = 1.4, bowing = 0.8) {
    # Validate geometry
    sf_data <- sf_data[!st_is_empty(sf_data), ]
    if (nrow(sf_data) == 0) {
        return(fallback_panel(year_label, annotation))
    }

    # CRITICAL: roughsf does not support MULTI* geometries — cast to POLYGON
    sf_data <- tryCatch(
        st_cast(sf_data, "POLYGON"),
        error = function(e) sf_data
    )
    sf_data <- st_make_valid(sf_data)
    sf_data <- sf_data[!st_is_empty(sf_data), ]
    if (nrow(sf_data) == 0) {
        return(fallback_panel(year_label, annotation))
    }

    n <- nrow(sf_data)
    # as.character() strips the palette class that breaks jsonlite serialisation
    fills <- as.character(met.brewer(palette_name, n = n, type = "continuous"))

    # Styling via columns — exact names from roughsf docs:
    # fill, stroke (numeric width), fillweight, fillstyle
    sf_data$fill <- fills
    sf_data$stroke <- rep(1.2, n)
    sf_data$fillweight <- rep(0.6, n)
    sf_data$fillstyle <- rep("solid", n)

    # roughsf() takes a LIST of sf objects
    p <- tryCatch(
        roughsf(
            list(sf_data),
            roughness      = roughness,
            bowing         = bowing,
            simplification = 1,
            width          = 600,
            height         = 500
        ),
        error = function(e) {
            message(
                "  roughsf failed for ", year_label, ": ", e$message,
                " — using ggplot2 fallback"
            )
            NULL
        }
    )

    # roughsf returns an htmlwidget
    # Save to a temp PNG via webshot2 then read back as ggplot image
    if (!is.null(p) && requireNamespace("webshot2", quietly = TRUE)) {
        tmp_html <- tempfile(fileext = ".html")
        tmp_png <- tempfile(fileext = ".png")

        tryCatch(
            {
                # Save widget as self-contained HTML
                htmlwidgets::saveWidget(p, tmp_html,
                    selfcontained = TRUE,
                    background = "#fff8f2"
                )
                # Screenshot to PNG — white background
                webshot2::webshot(
                    url = paste0("file:///", normalizePath(tmp_html, winslash = "/")),
                    file = tmp_png,
                    vwidth = 600,
                    vheight = 500,
                    delay = 0.5,
                    cliprect = c(0, 0, 600, 500)
                )

                if (file.exists(tmp_png) && file.size(tmp_png) > 1000) {
                    img <- png::readPNG(tmp_png)
                    p_gg <- ggplot() +
                        annotation_raster(img, xmin = 0, xmax = 1, ymin = 0, ymax = 1) +
                        coord_fixed(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE) +
                        labs(title = year_label, caption = annotation) +
                        panel_theme() +
                        theme(plot.background = element_rect(
                            fill = "#fff8f2", color = "#e0d8d0",
                            linewidth = 0.4
                        ))
                    return(p_gg)
                }
            },
            error = function(e) {
                message("  webshot2 capture failed: ", e$message)
            }
        )
    }

    # ggplot2 fallback — plain geom_sf with MetBrewer palette
    message("  Using ggplot2 fallback for ", year_label)
    sf_data$fill_col <- fills
    ggplot(sf_data) +
        geom_sf(aes(fill = fill_col),
            color = "#3d3530",
            linewidth = 0.5, show.legend = FALSE
        ) +
        scale_fill_identity() +
        labs(title = year_label, caption = annotation) +
        panel_theme()
}

fallback_panel <- function(year_label, annotation) {
    ggplot() +
        labs(title = year_label, caption = annotation) +
        panel_theme()
}
```

## GeoJSON Export

Country boundaries are exported to JavaScript data structures so the interactive animation can draw them in the browser without any server dependency.

```{r export_geojson}
export_region_json <- function(region_key) {
    reg <- regions[[region_key]]
    result <- list()

    for (i in seq_along(reg$years)) {
        yr <- as.character(reg$years[i])
        dt <- reg$dates[i]
        ann <- reg$annotations[yr]

        sf_data <- tryCatch(
            get_region_sf(dt, reg$bbox, region_key = region_key),
            error = function(e) NULL
        )

        if (is.null(sf_data) || nrow(sf_data) == 0) {
            result[[i]] <- list(year = yr, annotation = ann, countries = list())
            next
        }

        # Simplify geometries before JSON export — reduces file size for the browser widget
        # dTolerance = 0.05 degrees (~5km) preserves country shapes without over-burdening the canvas
        sf_simple <- st_simplify(sf_data, dTolerance = 0.05)
        n <- nrow(sf_simple)
        fills <- as.character(met.brewer("Redon", n = n, type = "continuous"))

        name_col <- intersect(
            c("country_name", "CNTRY_NAME", "name", "NAME"),
            names(sf_simple)
        )
        name_col <- if (length(name_col) > 0) name_col[1] else NA_character_

        countries <- lapply(seq_len(n), function(j) {
            # Export as FeatureCollection — JS extractGeom() handles this
            gj_text <- geojsonsf::sf_geojson(sf_simple[j, ])
            # Parse back to R list so jsonlite can re-serialise into the parent JSON
            gj_obj <- jsonlite::fromJSON(gj_text, simplifyVector = FALSE)
            list(
                name = if (!is.na(name_col)) {
                    as.character(sf_simple[[name_col]][j])
                } else {
                    paste("Country", j)
                },
                fill = fills[j],
                geojson = gj_obj # FeatureCollection — JS allGeoms() handles all types
            )
        })

        result[[i]] <- list(year = yr, annotation = ann, countries = countries)
    }
    result
}

for (rk in names(regions)) {
    message("Exporting GeoJSON for ", rk)
    data <- export_region_json(rk)
    json <- jsonlite::toJSON(data, auto_unbox = TRUE, pretty = FALSE)
    js_var <- paste0(
        "var REGION_", toupper(gsub("-", "_", rk)), " = ", json, ";"
    )
    writeLines(js_var, paste0("outputs/data_", rk, ".js"))
    message("  Saved: outputs/data_", rk, ".js")
}
```

## Interactive Animation

The animation widget is built entirely in R — `rough.js` is loaded from the `roughsf` package installation (no CDN, no network dependency), GeoJSON data is embedded directly, and the result is a single self-contained HTML file. The JavaScript draws each country's polygon onto a `<canvas>` element using the `rough.js` API, replicating the hand-drawn aesthetic in the browser.

```{r build_animation_html}
#| code-fold: true
#| code-summary: "Show animation builder (HTML/JavaScript — 400 lines)"
# Load rough.js from the roughsf package installation — zero network, zero hardcoding
# roughsf ships rough.js at inst/htmlwidgets/lib/rough/rough.js
rough_js_src <- tryCatch(
    {
        p <- system.file("htmlwidgets", "lib", "rough", "rough.js", package = "roughsf")
        if (nchar(p) == 0 || !file.exists(p)) stop("not found via system.file")
        src <- paste(readLines(p, warn = FALSE), collapse = "\n")
        message("rough.js loaded from roughsf package: ", p, " (", nchar(src), " chars)")
        src
    },
    error = function(e) {
        # Fallback: search all R library paths
        for (lib in .libPaths()) {
            p <- file.path(lib, "roughsf", "htmlwidgets", "lib", "rough", "rough.js")
            if (file.exists(p)) {
                src <- paste(readLines(p, warn = FALSE), collapse = "\n")
                message("rough.js found at: ", p)
                return(src)
            }
        }
        stop(paste0(
            "rough.js not found inside roughsf package.\n",
            "Ensure roughsf is installed: install.packages('roughsf')\n",
            "Searched: ", paste(.libPaths(), collapse = ", ")
        ))
    }
)

read_js_file <- function(rk) {
    path <- paste0("outputs/data_", rk, ".js")
    if (file.exists(path)) {
        paste(readLines(path, warn = FALSE), collapse = "\n")
    } else {
        paste0("var REGION_", toupper(rk), " = [];")
    }
}

js_ce <- read_js_file("central_europe")
js_me <- read_js_file("middle_east")
js_af <- read_js_file("africa")

html_lines <- c(
    "<!DOCTYPE html>",
    "<html lang='en'>",
    "<head>",
    "<meta charset='UTF-8'>",
    "<meta name='viewport' content='width=device-width, initial-scale=1.0'>",
    "<title>Lines of Intent</title>",
    "<style>",
    "* { box-sizing: border-box; margin: 0; padding: 0; }",
    "body { background: #faf8f4; font-family: Georgia, serif;",
    "  display: flex; flex-direction: column; align-items: center; padding: 28px 16px 20px; }",
    ".title-block { text-align: center; margin-bottom: 20px; }",
    ".title-block h1 { font-size: 32px; font-weight: bold; color: #2a2420;",
    "  letter-spacing: -0.5px; margin-bottom: 4px; }",
    ".title-block p { font-size: 11px; color: #9a8e88; margin-bottom: 10px; }",
    ".title-block .intro { font-size: 12px; color: #5a4e48; max-width: 640px;",
    "  line-height: 1.65; margin: 0 auto; }",
    ".rbar { display: flex; gap: 8px; margin-bottom: 10px; flex-wrap: wrap; justify-content: center; }",
    ".rbtn { background: transparent; border: 0.5px solid #c0b4a8; border-radius: 6px;",
    "  padding: 6px 16px; font-family: Georgia, serif; font-size: 11px;",
    "  color: #3d3530; cursor: pointer; transition: all 0.2s; }",
    ".rbtn:hover { background: rgba(0,0,0,0.04); }",
    ".rbtn.active { font-weight: bold; }",
    ".rbtn.active.ce  { border-color: #6B8F71; color: #6B8F71; background: rgba(107,143,113,0.08); }",
    ".rbtn.active.me  { border-color: #B07D4A; color: #B07D4A; background: rgba(176,125,74,0.08); }",
    ".rbtn.active.af  { border-color: #A85C52; color: #A85C52; background: rgba(168,92,82,0.08); }",
    ".story { font-size: 11px; color: #5a4e48; max-width: 700px; width: 100%;",
    "  line-height: 1.6; padding: 10px 14px; border-radius: 0 6px 6px 0;",
    "  margin-bottom: 14px; transition: border-color 0.3s, background 0.3s; }",
    ".story.ce { border-left: 3px solid #6B8F71; background: rgba(107,143,113,0.06); }",
    ".story.me { border-left: 3px solid #B07D4A; background: rgba(176,125,74,0.06); }",
    ".story.af { border-left: 3px solid #A85C52; background: rgba(168,92,82,0.06); }",
    ".ctrls { display: flex; gap: 8px; justify-content: center;",
    "  align-items: center; margin-bottom: 10px; flex-wrap: wrap; }",
    ".ctrl { background: transparent; border: 0.5px solid #c0b4a8; border-radius: 6px;",
    "  padding: 5px 14px; font-family: Georgia, serif; font-size: 11px;",
    "  color: #3d3530; cursor: pointer; transition: background 0.15s; }",
    ".ctrl:hover { background: rgba(0,0,0,0.04); }",
    ".ctrl#pbtn { font-weight: bold; }",
    ".sbar { display: flex; justify-content: space-between; align-items: center;",
    "  width: 100%; max-width: 900px; padding: 4px 10px;",
    "  background: rgba(0,0,0,0.025); border-radius: 6px; margin-bottom: 10px;",
    "  font-size: 10px; color: #9a8e88; }",
    "#prog { font-weight: bold; color: #3d3530; }",
    ".spd { display: flex; align-items: center; gap: 8px;",
    "  font-size: 10px; color: #9a8e88; margin-bottom: 10px; }",
    ".spd input { width: 90px; }",
    ".prow { display: flex; align-items: center; justify-content: center;",
    "  gap: 4px; margin-bottom: 10px; }",
    ".pip { width: 9px; height: 9px; border-radius: 50%; background: #d4c8bc;",
    "  transition: background 0.4s, transform 0.3s; cursor: pointer; }",
    ".pip.lit  { background: #3d3530; transform: scale(1.3); }",
    ".pip.done { background: #a09060; transform: scale(1.1); }",
    ".psep { font-size: 8px; color: #c8beb8; }",
    ".grid { display: grid; grid-template-columns: repeat(3, 1fr);",
    "  gap: 8px; width: 100%; max-width: 900px; margin-bottom: 12px; }",
    ".card { background: #fff8f2; border-radius: 8px; border: 0.5px solid #e0d8d0;",
    "  padding: 7px 6px 6px; opacity: 1; min-height: 240px;",
    "  transition: opacity 0.4s ease, box-shadow 0.4s ease;",
    "  display: flex; flex-direction: column; align-items: center; }",
    ".card.active { border-color: var(--accent, #c0b4a8); }",
    ".card.ce-card.active { border-color: #6B8F71; border-width: 1.5px; }",
    ".card.me-card.active { border-color: #B07D4A; border-width: 1.5px; }",
    ".card.af-card.active { border-color: #A85C52; border-width: 1.5px; }",
    ".card.pulse { box-shadow: 0 0 14px rgba(160,130,80,0.38); }",
    ".card.ce-card { border-color: #6B8F71; }",
    ".card.me-card { border-color: #B07D4A; }",
    ".card.af-card { border-color: #A85C52; }",
    ".ytag { font-size: 14px; font-weight: bold; color: #5a4e48;",
    "  text-align: center; margin-bottom: 3px; transition: color 0.3s; }",
    ".ytag.pulse { color: #8a6a30; }",
    "canvas { width: 100%; height: auto; aspect-ratio: 280/200; display: block; }",
    ".panel-bottom { display: flex; gap: 8px; width: 100%; margin-top: 4px; min-height: 60px; }",
    ".clist { flex: 1; min-width: 0; }",
    ".pannot { flex: 1; min-width: 0; display: flex; align-items: center;",
    "  justify-content: center; padding: 6px 4px 6px 12px; align-items: flex-start;",
    "  opacity: 0; transition: opacity 0.6s ease; }",
    ".pannot.visible { opacity: 1; }",
    ".pannot-text { font-family: Georgia, serif; font-size: 11px;",
    "  color: #3d3530; font-style: italic; font-weight: bold;",
    "  line-height: 1.6; text-align: left; }",
    ".clist { width: 100%; min-height: 44px; }",
    ".citem { display: flex; align-items: center; gap: 5px; margin-bottom: 2px;",
    "  animation: np 0.3s ease forwards; opacity: 0; }",
    "@keyframes np { from{opacity:0;transform:translateY(3px)} to{opacity:1;transform:translateY(0)} }",
    ".cdot { width: 7px; height: 7px; border-radius: 50%; flex-shrink: 0;",
    "  border: 0.5px solid rgba(0,0,0,0.15); }",
    ".cname { font-size: 7.5px; color: #3d3530; font-weight: 500; line-height: 1.3; }",
    ".brow { width: 100%; display: flex; justify-content: flex-start;",
    "  align-items: center; margin-top: 2px; }",
    ".bcount { font-family: Georgia, serif; font-weight: bold; color: #3d3530;",
    "  transition: font-size 0.4s ease, color 0.4s ease;",
    "  font-size: 13px; margin-bottom: 2px; display: block; }",
    ".bcount.growing { color: #6B8F71; }",
    ".drag-handle { text-align: center; font-size: 9px; color: #c8beb8; letter-spacing: 2px;",
    "  cursor: grab; user-select: none; width: 100%; margin-bottom: 2px; padding: 1px 0;",
    "  border-radius: 4px; transition: color 0.2s, background 0.2s; }",
    ".drag-handle:hover { color: #9a8e88; background: rgba(0,0,0,0.04); }",
    ".drag-handle:active { cursor: grabbing; }",
    ".card.drag-over { border-style: dashed !important; opacity: 0.65; }",
    ".card.dragging { opacity: 0.35; }",
    ".tip { position: fixed; background: #2a2420; color: #faf8f4;",
    "  font-family: Georgia, serif; font-size: 10px; padding: 5px 9px;",
    "  border-radius: 5px; pointer-events: none; opacity: 0;",
    "  transition: opacity 0.15s; z-index: 9999; max-width: 180px;",
    "  line-height: 1.4; }",
    ".tip.visible { opacity: 1; }",
    ".cap { font-size: 9px; color: #c0b4a8; text-align: center;",
    "  margin-top: 8px; line-height: 1.6; }",
    "</style></head><body>",
    "<div class='title-block'>",
    "  <h1>Lines of Intent</h1>",
    "  <p>Every Border Was Someone&#39;s Decision</p>",
    "  <p class='intro'>Borders are not natural facts. They were drawn by people, in rooms, on specific dates &mdash; and they can be redrawn. Watch three regions of the world get redrawn across the twentieth century.</p>",
    "</div>",
    "<div class='rbar'>",
    "  <button class='rbtn active ce' onclick=\"loadRegion('central_europe',this)\">Central Europe</button>",
    "  <button class='rbtn me' onclick=\"loadRegion('middle_east',this)\">Middle East</button>",
    "  <button class='rbtn af' onclick=\"loadRegion('africa',this)\">Post-colonial Africa</button>",
    "</div>",
    "<div class='story ce' id='story'>One empire controlled this land in 1914. By 2000 it had fractured into 15 countries. Watch the same territory get redrawn by war, defeat, and ideology across eight decades.</div>",
    "<div class='ctrls'>",
    "  <button class='ctrl' onclick='replayPanel()'>&#x21BA; replay</button>",
    "  <button class='ctrl' id='pbtn' onclick='togglePlay()'>play</button>",
    "  <button class='ctrl' onclick='nextPanel()'>next &#x2192;</button>",
    "</div>",
    "<div class='spd'>",
    "  <span>speed</span>",
    "  <input type='range' id='spdr' min='1' max='5' value='5' oninput='setSpd(this.value)'>",
    "  <span id='spdl'>very fast</span>",
    "</div>",
    "<div class='sbar'><span id='stat'>press play to begin</span><span id='prog'></span></div>",
    "<div class='grid' id='grid'></div>",
    "<div class='prow' id='prow'></div>",
    "<div class='tip' id='tip'></div>",
    "<div class='cap'>",
    "  Data: cshapes R package (Weidmann et al., 2010) &middot; Rendered with roughsf &middot; Palette: MetBrewer Redon",
    "</div>",
    paste0("<script>", rough_js_src, "</script>"),
    "<script>",
    js_ce,
    js_me,
    js_af,
    "var RM={central_europe:REGION_CENTRAL_EUROPE,middle_east:REGION_MIDDLE_EAST,africa:REGION_AFRICA};",
    "var RS={",
    "  central_europe:'One empire controlled this land in 1914. By 2000 it had fractured into 15 countries. Watch the same territory get redrawn by war, defeat, and ideology across eight decades.',",
    "  middle_east:'In 1916 two men drew lines on a map in London and divided the Middle East between Britain and France. Those Sykes-Picot borders still shape the region today.',",
    "  africa:'In 1938 only 4 countries existed on this continent — the rest was under colonial rule. By 1993 there were 54. Look carefully: the borders barely moved. The lines drawn in Berlin in 1884 are still the lines of today. That IS the story.'",
    "};",
    "var RC={central_europe:'ce',middle_east:'me',africa:'af'};",
    "var currentRegion='central_europe';",
    "var FR=REGION_CENTRAL_EUROPE,yi=0,ci=0,playing=false,pausing=false,tmr=null,spd=250;",
    "var SL={1:'very slow',2:'slow',3:'normal',4:'fast',5:'very fast'};",
    "var SV={1:1800,2:1200,3:900,4:500,5:250};",
    "var CBBOX={};",
    "function setSpd(v){spd=SV[v];document.getElementById('spdl').textContent=SL[v];}",
    "function buildGrid(){",
    "  var g=document.getElementById('grid');g.innerHTML='';",
    "  var pr=document.getElementById('prow');pr.innerHTML='';",
    "  CBBOX={};",
    "  var rgc=RC[currentRegion]||'ce';",
    "  FR.forEach(function(f,i){",
    "    var card=document.createElement('div');",
    "    card.className='card '+rgc+'-card';card.id='card-'+i;",
    "    card.setAttribute('ondragover','onDragOver(event,'+i+')');",
    "    card.setAttribute('ondrop','onDrop(event,'+i+')');",
    "    var dh=document.createElement('div');dh.className='drag-handle';",
    "    dh.setAttribute('draggable','true');dh.title='Drag to reorder';",
    "    dh.setAttribute('ondragstart','onDragStart(event,'+i+')');",
    "    dh.setAttribute('ondragend','onDragEnd(event,'+i+')');",
    "    dh.textContent='\u22ee\u22ee';card.appendChild(dh);",
    "    var tag=document.createElement('div');tag.className='ytag';tag.id='tag-'+i;",
    "    tag.textContent=f.year;card.appendChild(tag);",
    "    var cv=document.createElement('canvas');cv.id='cv-'+i;cv.width=280;cv.height=200;",
    "    cv.setAttribute('data-key',f.year);",
    "    card.appendChild(cv);",
    "    var br=document.createElement('div');br.className='brow';",
    "    var bc=document.createElement('span');bc.className='bcount';bc.id='bc-'+i;",
    "    bc.textContent='';",
    "    br.appendChild(bc);card.appendChild(br);",
    "    var pb=document.createElement('div');pb.className='panel-bottom';",
    "    var cl=document.createElement('div');cl.className='clist';cl.id='cl-'+i;",
    "    pb.appendChild(cl);",
    "    var pa=document.createElement('div');pa.className='pannot';pa.id='pannot-'+i;",
    "    var pt=document.createElement('div');pt.className='pannot-text';",
    "    pt.textContent='\u201c'+( f.annotation||'')+'\u201d';",
    "    pa.appendChild(pt);pb.appendChild(pa);",
    "    card.appendChild(pb);",
    "    g.appendChild(card);",
    "    var pip=document.createElement('span');pip.className='pip';pip.id='pip-'+i;",
    "    pr.appendChild(pip);",
    "    if(i<FR.length-1){var s=document.createElement('span');s.className='psep';s.textContent='—';pr.appendChild(s);}",
    "  });",
    "  setupCanvasHover();",
    "}",
    "function allGeoms(gj){",
    "  var r=[];if(!gj)return r;",
    "  if(Array.isArray(gj)){gj.forEach(function(x){allGeoms(x).forEach(function(g){r.push(g);});});return r;}",
    "  if(gj.type==='FeatureCollection'&&gj.features)",
    "    gj.features.forEach(function(f){if(f&&f.geometry)r.push(f.geometry);});",
    "  else if(gj.type==='Feature'&&gj.geometry) r.push(gj.geometry);",
    "  else if(gj.type==='Polygon'||gj.type==='MultiPolygon') r.push(gj);",
    "  return r;",
    "}",
    "function flatP(g){",
    "  var r=[];if(!g)return r;",
    "  if(g.type==='Polygon'&&g.coordinates&&g.coordinates[0]) r.push(g.coordinates[0]);",
    "  else if(g.type==='MultiPolygon'&&g.coordinates)",
    "    g.coordinates.forEach(function(p){if(p&&p[0]&&p[0].length>2)r.push(p[0]);});",
    "  return r;",
    "}",
    "function allCoords(cs){",
    "  var r=[];if(!cs)return r;",
    "  cs.forEach(function(c){",
    "    if(!c||!c.geojson)return;",
    "    allGeoms(c.geojson).forEach(function(g){",
    "      flatP(g).forEach(function(ring){ring.forEach(function(p){if(p&&p.length>=2)r.push(p);});});",
    "    });",
    "  });return r;",
    "}",
    "function bounds(cs){",
    "  var c=allCoords(cs);",
    "  if(!c.length)return{x0:-10,x1:30,y0:44,y1:56};",
    "  return{x0:Math.min.apply(null,c.map(function(p){return p[0];})),",
    "         x1:Math.max.apply(null,c.map(function(p){return p[0];})),",
    "         y0:Math.min.apply(null,c.map(function(p){return p[1];})),",
    "         y1:Math.max.apply(null,c.map(function(p){return p[1];}))};",
    "}",
    "function drawC(pi,cd,cb){",
    "  var cv=document.getElementById('cv-'+pi);if(!cv){if(cb)cb();return;}",
    "  if(typeof rough==='undefined'){if(cb)cb();return;}",
    "  var rc=rough.canvas(cv);if(!rc){if(cb)cb();return;}",
    "  var b=bounds(FR[pi].countries);",
    "  var W=cv.width,H=cv.height,P=12;",
    "  function pr(lon,lat){",
    "    return[P+(lon-b.x0)/(b.x1-b.x0)*(W-2*P),",
    "           H-P-(lat-b.y0)/(b.y1-b.y0)*(H-2*P)];",
    "  }",
    "  var geoms=allGeoms(cd.geojson);",
    "  if(!geoms.length){if(cb)cb();return;}",
    "  var pts=[];",
    "  geoms.forEach(function(g){",
    "    flatP(g).forEach(function(ring){",
    "      var mapped=ring.map(function(c){return pr(c[0],c[1]);});",
    "      pts=pts.concat(mapped);",
    "      try{rc.polygon(mapped,{fill:cd.fill||'#c9b99a',fillStyle:'solid',fillWeight:0.6,",
    "        stroke:'#3d3530',strokeWidth:1.3,roughness:1.4,bowing:0.8});}catch(e){}",
    "    });",
    "  });",
    "  if(pts.length>0){",
    "    var xs=pts.map(function(p){return p[0];}),ys=pts.map(function(p){return p[1];});",
    "    var yk=FR[pi]?FR[pi].year:String(pi);",
    "    if(!CBBOX[yk])CBBOX[yk]=[];",
    "    CBBOX[yk].push({",
    "      name:cd.name,fill:cd.fill,",
    "      x0:Math.min.apply(null,xs),x1:Math.max.apply(null,xs),",
    "      y0:Math.min.apply(null,ys),y1:Math.max.apply(null,ys)",
    "    });",
    "  }",
    "  addLbl(pi,cd.name,cd.fill||'#c9b99a');",
    "  updCnt(pi);",
    "  if(cb)setTimeout(cb,20);",
    "}",
    "function setupCanvasHover(){",
    "  var tip=document.getElementById('tip');",
    "  FR.forEach(function(f,pi){",
    "    var cv=document.getElementById('cv-'+pi);",
    "    if(!cv)return;",
    "    cv.addEventListener('mousemove',function(e){",
    "      var rect=cv.getBoundingClientRect();",
    "      var scaleX=cv.width/rect.width,scaleY=cv.height/rect.height;",
    "      var mx=(e.clientX-rect.left)*scaleX,my=(e.clientY-rect.top)*scaleY;",
    "      var yk=cv.getAttribute('data-key')||String(pi);",
    "      var boxes=CBBOX[yk]||[];",
    "      var hit=null;",
    "      for(var i=boxes.length-1;i>=0;i--){",
    "        var bx=boxes[i];",
    "        if(mx>=bx.x0&&mx<=bx.x1&&my>=bx.y0&&my<=bx.y1){hit=bx;break;}",
    "      }",
    "      if(hit){",
    "        tip.textContent=(typeof NAME_MAP!=='undefined'?NAME_MAP[hit.name]||hit.name:hit.name);",
    "        tip.style.left=(e.clientX+12)+'px';",
    "        tip.style.top=(e.clientY-28)+'px';",
    "        tip.classList.add('visible');",
    "      } else {",
    "        tip.classList.remove('visible');",
    "      }",
    "    });",
    "    cv.addEventListener('mouseleave',function(){",
    "      document.getElementById('tip').classList.remove('visible');",
    "    });",
    "  });",
    "}",
    "var dragSrc=null;",
    "function onDragStart(e,i){",
    "  dragSrc=i;e.dataTransfer.effectAllowed='move';",
    "  setTimeout(function(){var c=document.getElementById('card-'+i);if(c)c.classList.add('dragging');},0);",
    "}",
    "function onDragEnd(e,i){",
    "  document.querySelectorAll('.card').forEach(function(c){c.classList.remove('dragging','drag-over');});",
    "}",
    "function onDragOver(e,i){",
    "  e.preventDefault();e.dataTransfer.dropEffect='move';",
    "  document.querySelectorAll('.card').forEach(function(c){c.classList.remove('drag-over');});",
    "  var c=document.getElementById('card-'+i);if(c&&dragSrc!==i)c.classList.add('drag-over');",
    "}",
    "function onDrop(e,dstIdx){",
    "  e.preventDefault();",
    "  document.querySelectorAll('.card').forEach(function(c){c.classList.remove('dragging','drag-over');});",
    "  if(dragSrc===null||dragSrc===dstIdx){dragSrc=null;return;}",
    "  var g=document.getElementById('grid');",
    "  var cards=Array.from(g.children);",
    "  var srcCard=cards[dragSrc],dstCard=cards[dstIdx];",
    "  if(dragSrc<dstIdx){g.insertBefore(srcCard,dstCard.nextSibling);}",
    "  else{g.insertBefore(srcCard,dstCard);}",
    "  var moved=FR.splice(dragSrc,1)[0];FR.splice(dstIdx,0,moved);",
    "  rebuildIds();dragSrc=null;",
    "}",
    "function rebuildIds(){",
    "  var g=document.getElementById('grid');",
    "  var cards=Array.from(g.children);",
    "  cards.forEach(function(card,i){",
    "    card.id='card-'+i;",
    "    var tag=card.querySelector('.ytag');if(tag)tag.id='tag-'+i;",
    "    var cv=card.querySelector('canvas');if(cv)cv.id='cv-'+i;",
    "    var bc=card.querySelector('.bcount');if(bc)bc.id='bc-'+i;",
    "    var cl=card.querySelector('.clist');if(cl)cl.id='cl-'+i;",
    "    var pa=card.querySelector('.pannot');if(pa)pa.id='pannot-'+i;",
    "    var dh=card.querySelector('.drag-handle');",
    "    if(dh){dh.setAttribute('ondragstart','onDragStart(event,'+i+')');",
    "            dh.setAttribute('ondragend','onDragEnd(event,'+i+')');}",
    "    card.setAttribute('ondragover','onDragOver(event,'+i+')');",
    "    card.setAttribute('ondrop','onDrop(event,'+i+')');",
    "  });",
    "  var pr=document.getElementById('prow');pr.innerHTML='';",
    "  FR.forEach(function(f,i){",
    "    var pip=document.createElement('span');pip.className='pip';pip.id='pip-'+i;",
    "    pr.appendChild(pip);",
    "    if(i<FR.length-1){var s=document.createElement('span');s.className='psep';s.textContent='\u2014';pr.appendChild(s);}",
    "  });",
    "}",
    "var NAME_MAP={",
    "  'Russia (Soviet Union)':'Russian Empire',",
    "  'Germany (Prussia)':'German Empire',",
    "  'Turkey (Ottoman Empire)':'Ottoman Empire',",
    "  'Iran (Persia)':'Persia (Iran)',",
    "  'Italy/Sardinia':'Italy',",
    "  'Tanzania (Tanganyika)':'Tanzania',",
    "  'Madagascar (Malagasy)':'Madagascar',",
    "  'Zimbabwe (Rhodesia)':'Zimbabwe',",
    "  'Swaziland (Eswatini)':'Eswatini',",
    "  'Burkina Faso (Upper Volta)':'Burkina Faso',",
    "  'Congo, Democratic Republic of (Zaire)':'DR Congo',",
    "  'Yemen (Arab Republic of Yemen)':'Yemen',",
    "  'German Federal Republic':'West Germany',",
    "  'German Democratic Republic':'East Germany'",
    "};",
    "function addLbl(pi,name,fill){",
    "  var l=document.getElementById('cl-'+pi);if(!l)return;",
    "  var it=document.createElement('div');it.className='citem';",
    "  var d=document.createElement('span');d.className='cdot';d.style.background=fill;",
    "  var n=document.createElement('span');n.className='cname';n.textContent=NAME_MAP[name]||name;",
    "  it.appendChild(d);it.appendChild(n);l.appendChild(it);",
    "}",
    "function updCnt(pi){",
    "  var f=FR[pi],el=document.getElementById('bc-'+pi);if(!el)return;",
    "  var l=document.getElementById('cl-'+pi);",
    "  var done=l?l.children.length:0,tot=f.countries?f.countries.length:0;",
    "  var prevDone=parseInt(el.getAttribute('data-prev')||'0');",
    "  el.setAttribute('data-prev',done);",
    "  el.textContent=done>=tot?tot+' countries':done+' / '+tot;",
    "  var sz=Math.round(13+((done-3)/(54-3))*13);",
    "  sz=Math.max(13,Math.min(26,sz));",
    "  el.style.fontSize=sz+'px';",
    "  if(done>prevDone&&done>1)el.classList.add('growing');",
    "  else el.classList.remove('growing');",
    "}",
    "function setPipLit(i){document.querySelectorAll('.pip').forEach(function(p,j){p.classList.toggle('lit',j===i);});}",
    "function setPipDone(i){var p=document.getElementById('pip-'+i);if(p){p.classList.remove('lit');p.classList.add('done');}}",
    "function pulse(i){",
    "  var c=document.getElementById('card-'+i),t=document.getElementById('tag-'+i);",
    "  if(!c||!t)return;",
    "  c.classList.add('pulse');t.classList.add('pulse');",
    "  setTimeout(function(){c.classList.remove('pulse');t.classList.remove('pulse');},1300);",
    "  var pa=document.getElementById('pannot-'+i);",
    "  if(pa){",
    "    var rc2=RC[currentRegion]||'ce';",
    "    var acols={ce:'#6B8F71',me:'#B07D4A',af:'#A85C52'};",
    "    pa.style.borderLeftColor=acols[rc2]||'#c0a888';",
    "    setTimeout(function(){pa.classList.add('visible');},300);",
    "  }",
    "}",
    "function tick(){",
    "  if(!playing||pausing)return;",
    "  var f=FR[yi];if(!f)return;",
    "  if(ci===0){",
    "    var c=document.getElementById('card-'+yi);if(c)c.classList.add('active');",
    "    setPipLit(yi);",
    "    document.getElementById('stat').textContent='drawing '+f.year+'...';",
    "  }",
    "  var cs=f.countries||[];",
    "  if(ci<cs.length){",
    "    drawC(yi,cs[ci],function(){",
    "      ci++;",
    "      document.getElementById('prog').textContent=(yi+1)+'/'+FR.length+' panels';",
    "      if(playing)tmr=setTimeout(tick,spd);",
    "    });",
    "  } else {",
    "    updCnt(yi);pulse(yi);setPipDone(yi);",
    "    document.getElementById('stat').textContent=f.year+' complete';",
    "    if(yi<FR.length-1){",
    "      pausing=true;",
    "      tmr=setTimeout(function(){pausing=false;yi++;ci=0;if(playing)tick();},1800);",
    "    } else {",
    "      playing=false;",
    "      document.getElementById('pbtn').textContent='play';",
    "      document.getElementById('stat').textContent='complete \u2014 all panels drawn';",
    "    }",
    "  }",
    "}",
    "function togglePlay(){",
    "  if(playing){",
    "    playing=false;clearTimeout(tmr);",
    "    document.getElementById('pbtn').textContent='play';",
    "    document.getElementById('stat').textContent='paused';",
    "  } else {",
    "    playing=true;",
    "    document.getElementById('pbtn').textContent='pause';",
    "    tick();",
    "  }",
    "}",
    "function nextPanel(){",
    "  clearTimeout(tmr);pausing=false;",
    "  var f=FR[yi];if(!f)return;",
    "  var c=document.getElementById('card-'+yi);if(c)c.classList.add('active');",
    "  var cs=f.countries||[];",
    "  function dn(i){",
    "    if(i>=cs.length){",
    "      updCnt(yi);pulse(yi);setPipDone(yi);",
    "      if(yi<FR.length-1){",
    "        pausing=true;",
    "        setTimeout(function(){pausing=false;yi++;ci=0;if(playing)tick();},600);",
    "      }",
    "      return;",
    "    }",
    "    drawC(yi,cs[i],function(){dn(i+1);});",
    "  }",
    "  dn(ci);ci=cs.length;",
    "}",
    "function replayPanel(){",
    "  clearTimeout(tmr);pausing=false;",
    "  var cv=document.getElementById('cv-'+yi);",
    "  if(cv){var ctx=cv.getContext('2d');ctx.clearRect(0,0,cv.width,cv.height);}",
    "  var cl=document.getElementById('cl-'+yi);if(cl)cl.innerHTML='';",
    "  var bc=document.getElementById('bc-'+yi);",
    "  if(bc){bc.textContent='';bc.removeAttribute('data-prev');}",
    "  var pa=document.getElementById('pannot-'+yi);if(pa)pa.classList.remove('visible');",
    "  var card=document.getElementById('card-'+yi);if(card){card.classList.remove('active','pulse');}",
    "  var pip=document.getElementById('pip-'+yi);if(pip){pip.classList.remove('lit','done');}",
    "  ci=0;playing=true;",
    "  document.getElementById('pbtn').textContent='pause';",
    "  document.getElementById('stat').textContent='replaying '+(FR[yi]?FR[yi].year:'')+'...';",
    "  tick();",
    "}",
    "function restart(){",
    "  clearTimeout(tmr);playing=false;pausing=false;yi=0;ci=0;",
    "  document.getElementById('pbtn').textContent='play';",
    "  document.getElementById('stat').textContent='press play to begin';",
    "  document.getElementById('prog').textContent='';",
    "  buildGrid();",
    "}",
    "function loadRegion(key,btn){",
    "  document.querySelectorAll('.rbtn').forEach(function(b){",
    "    b.classList.remove('active');",
    "  });",
    "  btn.classList.add('active');",
    "  var rc=RC[key]||'ce';",
    "  var story=document.getElementById('story');",
    "  if(story){story.className='story '+rc;story.textContent=RS[key]||'';}",
    "  currentRegion=key;",
    "  FR=RM[key]||REGION_CENTRAL_EUROPE;",
    "  restart();",
    "  togglePlay();",
    "}",
    "buildGrid();",
    "togglePlay();",
    "</script></body></html>"
)
writeLines(html_lines, "outputs/lines-of-intent-interactive.html")
message("Saved: outputs/lines-of-intent-interactive.html")
```

```{r export_gif, eval=FALSE}
# GIF export disabled — the interactive HTML is the primary deliverable.
# The animation requires user interaction (play button) so webshot2 frame capture produces blank frames.
# To generate a GIF manually: record the HTML animation using screen capture software.
if (requireNamespace("webshot2", quietly = TRUE) &&
    file.exists("outputs/lines-of-intent-interactive.html")) {
    html_path <- normalizePath("outputs/lines-of-intent-interactive.html")
    frames_dir <- "outputs/frames"

    # Fewer frames, fixed clip rect to keep all PNGs identical size
    frame_times <- seq(1, 35, by = 1.2)
    message("Capturing ", length(frame_times), " GIF frames...")

    for (i in seq_along(frame_times)) {
        tryCatch(
            webshot2::webshot(
                url      = paste0("file:///", html_path),
                file     = file.path(frames_dir, sprintf("frame_%03d.png", i)),
                delay    = frame_times[i],
                vwidth   = 900,
                vheight  = 680,
                cliprect = c(0, 0, 900, 680)
            ),
            error = function(e) NULL
        )
    }

    ffs <- sort(list.files(frames_dir, pattern = "\\.png$", full.names = TRUE))
    message("Found ", length(ffs), " frames")

    if (length(ffs) > 0) {
        # Standardise all frames to identical pixel dimensions
        if (requireNamespace("magick", quietly = TRUE)) {
            message("Standardising frame sizes...")
            for (ff in ffs) {
                tryCatch(
                    {
                        img <- magick::image_read(ff)
                        img <- magick::image_resize(img, "900x680!")
                        magick::image_write(img, path = ff, format = "png")
                    },
                    error = function(e) NULL
                )
            }
        }

        # gifski first, magick as fallback
        tryCatch(
            {
                gifski::gifski(
                    png_files = ffs,
                    gif_file  = "outputs/animation.gif",
                    width     = 900,
                    height    = 680,
                    delay     = 0.1
                )
                message("Saved: outputs/animation.gif")
            },
            error = function(e) {
                message("gifski failed: ", e$message)
                if (requireNamespace("magick", quietly = TRUE)) {
                    message("Trying magick fallback...")
                    imgs <- magick::image_read(ffs)
                    anim <- magick::image_animate(imgs, fps = 10, loop = 0)
                    magick::image_write(anim, path = "outputs/animation.gif")
                    message("Saved: outputs/animation.gif via magick")
                } else {
                    message("GIF skipped. Run: install.packages('magick') then re-render")
                }
            }
        )
    }
} else {
    message("Skipping GIF - webshot2 not installed")
}
```

```{r summary}
#| echo: false
cat("\n---- Output files ----\n")
for (f in c("outputs/lines-of-intent-interactive.html")) {
    if (file.exists(f)) {
        cat(sprintf("  OK   %-25s  %d KB\n", basename(f), round(file.size(f) / 1024)))
    } else {
        cat(sprintf("  MISS %-25s\n", basename(f)))
    }
}
```

---

## Interactive Visualization

Use the region buttons to switch between Central Europe, the Middle East, and Post-colonial Africa. The animation starts automatically. Hover over any country to see its name. Use **next →** to jump to the next panel, **↺ replay** to redraw the current panel, or drag the speed slider.

```{r display_animation}
#| echo: false
htmltools::includeHTML("outputs/lines-of-intent-interactive.html")
```

---

## Appendix — Reproducibility

```{r session_info}
#| code-fold: true
#| code-summary: "Show session info"
#| message: false
#| warning: false
sessionInfo()
```
